thesis2024

### 2025-05-07 index.qmd
Small post render changes

*Às mulheres da minha vida-a minha avó e a minha mãe-que sofreram e sacrificaram tudo o que podiam para me darem uma hipótese de um futuro mais feliz. Dei eu agora tudo o que tinha para vos deixar orgulhosas da criança que criaram.*

*There's a cycle here, a rhythm. Don't we need to know in advance if the next Season is going to be longer or worse somehow? How can we prepare for the future if we won't acknowledge the past?*

\- The stone sky, N. K. Jemisin

@@

Alright, now to the actual point; you already know what it is—after all, this is one of the first pages of a Doctoral dissertation, and it does say so in the title. But while the goal of this page—here we go, that science leaking from within my fingernails. Again, you have to forgive me... this is harder, much more complex than it seems (at least for me); after all, how do you fit within a few a pages nearly half a decade of appreciation for countless of people that made the colossal task of writing a doctoral dissertation—and all that goes between the lines—a pleasant, possible, plausible undertaking?

Let’s keep it simple then—thank you. All of you who shared my highs and my lows; who kept me afloat; who offered me advice, who gave me opportunities, who made me smile—all three families who helped me grow branches and sprout leaves, aiming towards the sky. And please forgive me if I chose to not name names. Hopefully I have done a proper job of thanking everyone who took part in this journey throughout the years.

@@

>>>>

@@

Alright, now to the actual point; you already know what it is—after all, this is one of the first pages of a Doctoral dissertation, and it does say so in the title. But while the goal of this page—here we go, that science leaking from within my fingernails. Again, you have to forgive me… this is harder, much more complex than it seems (at least for me); after all, how do you fit within a few a pages nearly half a decade of appreciation for countless of people that made the colossal task of writing a doctoral dissertation—and all that goes between the lines—a pleasant, possible, plausible undertaking?

Let’s keep it simple then—thank you. All of you who shared my highs and my lows; who kept me afloat; who offered me advice, who gave me opportunities, who made me smile—all three families (blood family, friend family, work family) who helped me grow branches and sprout leaves, aiming towards the sky. And please forgive me if I choose to not name names. Hopefully I have done a proper job of thanking everyone who took part in this journey throughout the years.

@@

Let me perhaps offer here a special thank you to someone who has been my teacher and supervisor for nearly a decade now, ever since I hopped inside his office back at the faculty, asking for something to learn and analyse; someone who has taught me more than lithics and articles and R—thank you, João. You and Célia have been my rocks—pun intended.
